---
title: "4C homework"
author: "Brago Aboagye-Nyame"
date: "7/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 4c. Transformations
```{r}
head(ChickWeight)
```

#### question 1
```{r}
hist(ChickWeight$weight)
```

The shape of the histogram tells us that chick weight is skewed to the right.

```{r}
hist(scale(ChickWeight$weight))
```

The shape of the histogram does not change

```{r}
qqnorm(ChickWeight$weight)
qqline(ChickWeight$weight, col= 'red')

qqnorm(scale(ChickWeight$weight))
qqline(scale(ChickWeight$weight), col= 'red')
```

The two are exactly the same except for the scale of the y axis. Since the points are mostly not on the line, this means that the distributions do not follow a normal distribution.

```{r}
library(tidyverse)
ChickWeight <- ChickWeight %>% transform(log_weight = log(weight), sqrt_weight = sqrt(weight))

qqnorm(ChickWeight$log_weight)
qqline(ChickWeight$log_weight, col= 'red')

qqnorm(ChickWeight$sqrt_weight)
qqline(ChickWeight$sqrt_weight, col= 'red')
```

Both transformations do a really good job normalizing the middle values of the data since they fall on the line pretty well but the tail ends of the transformed distribution are still nonnormal.

```{r}
library(caret)
bc_trans <- BoxCoxTrans(ChickWeight$weight, fudge= 0.05)
ChickWeight$bc_weight <- predict(bc_trans, ChickWeight$weight)

qqnorm(ChickWeight$bc_weight)
qqline(ChickWeight$bc_weight, col= 'red')
```

I'm noticing the same trend how the transformation does really well with the middle values but falters at the tails.

#### question 2
```{r}
normal_sample <- rnorm(1000, 0, 0.5)
qqnorm(normal_sample)
qqline(normal_sample, col= 'red')

exp_sample <- rexp(1000, 10)
qqnorm(exp_sample)
qqline(exp_sample, col= 'red')

log_exp_sample <- log(exp_sample)
qqnorm(log_exp_sample)
qqline(log_exp_sample, col= 'red')
```